Measuring Political Freedom Around the World

### 2020-11-11 slides.Rmd
table sized

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
library(kableExtra)
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE)
xaringanExtra::use_slide_tone()
```

>>>>

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
library(kableExtra)
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE)
# xaringanExtra::use_slide_tone()
```
